\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-28 doc/sui14/applications.tex
rewrote last sentence of applications section, fixed refs

%!TEX root = uist14.tex
\section{Applications}
\label{sec:applications}

@@

Our prototype includes three smart devices: a lamp and a fan that could be switched on and off; a smart TV with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). The on/off appliances are using relays, and the smart TV is a 30\inch{} display connected to a laptop. User interfaces for each were pre-defined in our application.

We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance.

@@

All participants successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous study procedure. Participants saw potential benefits of the device for families; one user remarked that he could imagine people using the system \studyquote{while keeping an eye on their children at the same time}.

% \bjoern{1 is problematic - because it sounds like that the head worn device is in the end not worth it and you should just use your phone, even if it takes longer. I'm not sure we can confidently say something about museums or body shops - this sounds speculative. Needs section needs to be rephrased., e.g. as in: Our solution succeeds at X because of Y. This suggests that future applications in domains like Z could be especially promising.}

\changes{Though our solution successfully solves the problem of {\em target selection}, we have not fully addressed the issue of controlling smart devices. One user reported that \studyquote{for more complex appliances (TV), interaction was more difficult}. A separate work on interaction techniques for head-worn computing devices is needed to address these issues, while we keep our focus on target selection.} \ben{ Suggest to remove this one: When the device is more complicated, it is possible that a better solution may be a hybrid -- to select the appliance with HOBS and control it with a phone.} \claire{ Is it possible to say that the number of complicated devices that you want to remote control is limited almost exclusively to the tv? I can't think of too many of these devices and our system works very well with more simple devices, which seem to be more common.} \sean{ I wouldn't state that. We could be challenged if the reviewers bring up smart fridge, microwave, etc.}

>>>>

%!TEX root = sui14.tex
\section{Applications}
\label{sec:applications}

@@

Our prototype includes three smart devices: a lamp and a fan that could be switched on and off; a smart TV with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). The on/off appliances are using relays, and the smart TV is a 30\inch{} display connected to a laptop. User interfaces for each were pre-defined in our application.
%
We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance.

@@

All participants successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous studies. Participants saw potential benefits of the device for families; one user remarked that he could imagine people using the system \studyquote{while keeping an eye on their children at the same time}.

% \bjoern{1 is problematic - because it sounds like that the head worn device is in the end not worth it and you should just use your phone, even if it takes longer. I'm not sure we can confidently say something about museums or body shops - this sounds speculative. Needs section needs to be rephrased., e.g. as in: Our solution succeeds at X because of Y. This suggests that future applications in domains like Z could be especially promising.}
\changes{While our system enabled users to select and control the example devices successfully, work remains in devising appropriate interfaces for complex devices. Users rated ease of use higher for the lamp and fan which had simple, discrete on/off actions, and lower for the TV control, which had more options. Multiple participants remarked that the difficulty was based on the affordances of Glass: \studyquote{Most of the difficulty I had with Glass came from having to navigate the interface on the tiny screen with the touch pad}. 
We leave addressing this fundamental usability challenge of wearable devices with near-eye displays to future work.}
%\changes{Though our solution successfully solves the problem of {\em target selection}, we have not fully addressed the issue of controlling smart devices. One user reported that \studyquote{for more complex appliances (TV), interaction was more difficult}. A separate work on interaction techniques for head-worn computing devices is needed to address these issues, while we keep our focus on target selection.} \ben{ Suggest to remove this one: When the device is more complicated, it is possible that a better solution may be a hybrid -- to select the appliance with HOBS and control it with a phone.} \claire{ Is it possible to say that the number of complicated devices that you want to remote control is limited almost exclusively to the tv? I can't think of too many of these devices and our system works very well with more simple devices, which seem to be more common.} \sean{ I wouldn't state that. We could be challenged if the reviewers bring up smart fridge, microwave, etc.}
